### 2018-05-28 VV570/HW1/assignment.tex
add another proof for the Cauchy-Schwarz inequality

\date{\normalsize\today} % Today's date or a custom date

@@

\begin{enumerate}
	\item
		\begin{proof}
			Let $E$ be an inner product space over $\mathbb{C}$, and $u, v\in E$.
			Given $Y$ defined as below, where $\lambda \in \mathbb{R}$.

@@

			\begin{equation}
				{\vert <u,v> \vert}^2 \leq \lVert u \rVert^2 \lVert v \rVert^2
			\end{equation}

		\end{proof}

>>>>

\date{\normalsize May 23, 2018} % Today's date or a custom date

@@

\begin{enumerate}
	\item
		Here I give 2 proofs, the first one comes directly from the class, the other from previous reading.(thanks to Ran Yi for pointing out that)

		\begin{proof}
			Let $E$ be an inner product space over $\mathbb{C}$, and $u, v\in E$.\\
			Given $Y$ defined as below, where $\lambda \in \mathbb{R}$.

@@

			\begin{equation}
				{\vert <u,v> \vert}^2 \leq \lVert u \rVert^2 \lVert v \rVert^2
			\end{equation}
		\end{proof}

		\begin{proof}
			Let $E$ be an inner product space over $\mathbb{C}$, and $u, v\in E$.\\

			Given $Y$ defined as below, where $\lambda \in \mathbb{R}$.

			\begin{equation}
				\begin{aligned}
					Y & = {\vert u-\lambda v \vert}^2 \\
					  & = <v, v>\lambda^2 -(<u, v>+<v, u>)\lambda + <u, u> \label{lbd}
				\end{aligned}
			\end{equation}

			It's obvious that $Y\geq0$ for any $\lambda$. \\
			Given $\lambda$ as
			\begin{equation}
				\lambda = \frac{<u,v>}{<v, v>}
			\end{equation}
			Substitude it into (\ref{lbd}), the inequality reads as
			\begin{equation}
				<u, u><v,v> - <u, v>(<u, v> + <v, u>) + <u, v>^2 \ \ \geq 0
			\end{equation}
			It can be further simplified as
			\begin{equation}
				\begin{aligned}
					<u, u> \cdot <v, v> \ \  & = ||u||^2 \cdot ||v||^2 \\
								        \ \  & \geq \ \ <u, v> \cdot <v, u>\\
								        \ \  & = \ \  <u, v> \cdot \overline{<u, v>}\\
								        \ \  & = \ \ |<u, v>|^2
				\end{aligned}
			\end{equation}

			Thus, the Cauchy-Schwarz inequality got proved.
		\end{proof}
